A Plasma Torus Around a Young Low-Mass Star

### 2025-01-20 paper/ms.tex
add essentials table

>>>>

\begin{table*}
\scriptsize
\setlength{\tabcolsep}{2pt}
\centering
\caption{Selected System Parameters for TIC~141146667}
\label{tab:params}
\begin{tabular}{llcc}
\hline \hline
Parameter & Description & Value & Source\\
\hline 
%
$T_{\rm eff}$\dotfill                   & Effective Temperature (K) \hspace{9pt}\dotfill                 & 2972 $\pm$ 40    & 1 \\
%$\log{g_{\star}}$\dotfill              & Surface Gravity (cgs)\hspace{9pt}\dotfill                      & 4.53 $\pm$ 0.05  & 6 \\
$R_\star$\dotfill                       & Stellar radius ($R_\odot$)\dotfill                             & 0.42$\pm$0.02    & 1 \\
%
$M_\star$\dotfill                       & Stellar mass ($M_\odot$)\dotfill                               & XXX  & 6 \\
%
Age                                     & Adopted stellar age (Myr)\dotfill                              & YYY  & 8 \\
%
Spec. Type\dotfill                      & Spectral Type\dotfill                                          & MXV              & X \\
%
$P_{\rm rot}$\dotfill                   & Rotation period (hr)\dotfill                                   & $3.930\pm 0.001$ & X \\
%
$v_{\rm eq}$\dotfill		                & Equatorial velocity \dotfill                                   &  130$\pm$4       & - \\
                                        & \hspace{3pt} ($2\pi R_\star/P_{\rm rot}$) (\kms)	             &                      \\
%
$v_{\rm eq}\sin{i_\star}$\dotfill		    & Projected rotational\dotfill                                   &  128$\pm$3       & X \\
                                        & \hspace{3pt} velocity (\kms)	                                 &                      \\
%
$i_\star$\dotfill                       & Stellar inclination (deg)\dotfill                              & 	XXX             & X \\
%
$d$\dotfill                             & Distance (pc)\dotfill                                          & $57.6 \pm X.X$   & X \\
%
$R_{\rm c}$\dotfill		                  & Keplerian corotation\dotfill                                   &  XXX             & X \\
                                        & \hspace{3pt} radius ($R_\star$)	                               &                      \\
%
$a_1$\dotfill                           & Clump 1 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  2.1-2.7         & X \\
$a_2$\dotfill                           & Clump 2 orbital radius ($R_\star$)\hspace{9pt}\dotfill         &  3.9             & X \\
%
$\langle$EW$_{\rm H\alpha}$$\rangle$    & Time-averaged H$\alpha$ line core                              &  X.X             & Y \\ 
                                        & \hspace{3pt} equivalent width (\AA)	                           &                      \\
Range(EW$_{\rm H\alpha}$)$_1$           & H$\alpha$ equiv. width range                                   &  X.X             & Y \\ 
                                        & \hspace{3pt} from Clump 1 (\AA)	                               &                      \\
Range(EW$_{\rm H\alpha}$)$_2$           & H$\alpha$ equiv. width range                                   &  X.X             & Y \\ 
                                        & \hspace{3pt} from Clump 2 (\AA)	                               &                      \\
\hline
\end{tabular}
\begin{flushleft}
\footnotesize{ \textsc{NOTE}---
%$^\dagger$ The GAIADR2 and GAIAEDR3 identifiers for Kepler 1627A are identical.  The secondary
is not resolved in the Gaia point source catalog.
$^*$ Given only $v\sin i$ and $2\pi R_\star/P_{\rm rot}$, $\cos i=0.11^{+0.11}_{-0.08}$.
Provenances are:
1: SED fit\cite{Bouma2024},
%$^6$Cluster isochrone (MIST adopted; PARSEC compared for quoted
%  uncertainty),
2: TESS light curve,
%  3: HIRES spectra and specmatch(?),
%$^8$Pre-main-sequence CAMD interpolation (Section~\ref{sec:camd}),
}
\end{flushleft}
\vspace{-0.5cm}
\end{table*}
